Technique for \earlywarning\ detection of compact binary coalescence and its implication for multimessenger astronomy

### 2011-06-01 results.tex
filled in some text
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@811 ccdd05d5-56c1-461a-bf98-85f6876523b4

\begin{figure}
\includegraphics{resamp_mm.pdf}
\caption{\label{fig:resamp_mm}}
\end{figure}

>>>>

We expect two contributions to the \SNR\ loss to arise in our implementation of
the \lloid\ algorithm.  The first is the \SNR\ loss due to the truncation of
the SVD basis, which is fundamental, and estimates for it
exist~\cite{Cannon:2010p10398}.  The second comes from non ideal
implementations of resampling that cause signal loss.  We have measured the
effect of the resampling in the pipeline alone on a single waveform to gauge
the magnitude of the loss.  It is shown in figure \ref{fig:resamp_mm} as a
function of the quality of the {\tt audioresample} element (which is
proportional to the filter length used).  In both cases we have to compare the
\SNR\ loss to the expected \SNR\ loss that arises from the discreteness of the
template bank which is typically $\sim 3\%$.  We will consider a comparable
\SNR\ loss to be tolerable, but ideally would like to have a factor of 10 lower
loss from the \lloid\ implementation (i.e. no more than $\sim 0.3 \%$).  
%
\begin{figure}
\includegraphics{resamp_mm.pdf}
\caption{\label{fig:resamp_mm}Mis-match as a function of the {\tt
audioresample} element's quality parameter.  Increasing the quality changes the
length of the sinc function filter that is used to decimate and interpolate the
data and filter output in our test pipeline.  Choosing a quality of 4
corresponds to a filter length of 64 samples and results in an acceptable loss
of .2 \% in \SNR\ for the chosen waveform.}
\end{figure}
